---
title: "MUsh"
author: "Sheetal"
date: "11/17/2018"
output: html_document
---

read the dataset and checked the column data.

```{r setup, include=FALSE}
Mush1 <- read.csv("train.csv")
dim(Mush1)
#Mush1<-Mush1[,2:24]
#unique(Mush1$V1)
```

## R Markdown

Converted the data into binary data.

```{r cars}

break_columns<-function(Mush_df)
{
  Mush_df<-Mush_df[,2:24]
for (i in colnames(Mush_df))
{
  if(i!="V1") {
 
  x<-unique(Mush_df[[i]])
  len<-length(x)
  
  if (len>=2) {
    for (K in 1:len){
      new_col<-paste0(i,"_",x[K])
      Mush_df[[new_col]]<- Mush_df[[i]]
      Mush_df[[new_col]]<-ifelse(Mush_df[[i]]==x[K],1,0)
    }
  
  }
  }
}
  Mush_df<-Mush_df[c(1,24:138)]
  return(Mush_df)
}
#Mush<-Mush[,24:118]
```

## Including Plots

removed the initial data 

```{r pressure, echo=FALSE}
#Mush[ -c(1, 3:6, 12) ]
#head(Mush)
Mush<-break_columns(Mush1)


```

Calculated entorpy of the dataset to identify the column which will give better result while classiffying.

```{r}

Entropy<-list()
j=0
for (i in colnames(Mush)){
  if(i!="V1") {
  E<-table(Mush[[i]],Mush$V1)
  S<-nrow(E)
  Ent<-0
  for( K in 1:S) {
    if(E[2,K]!=0){
  Ent =E[2,K]/sum(E[2,])*log(1/(E[2,K]/sum(E[2,])))+Ent
    }
  }
   Entropy[j]<-Ent
  j=j+1
}
  }
```

Calculated Gini_index of the dataset to identify the column which will give better result while classiffying.


```{r}

Gini_index<-list()
j=0
for (i in colnames(Mush)){
  if(i!="V1") {
  E<-table(Mush[[i]],Mush$V1)
  S<-nrow(E)
  Ent<-0
  for( K in 1:S) {
    if(E[2,K]!=0){
  Ent =E[2,K]/sum(E[2,])*E[2,K]/sum(E[2,])+Ent
    }
  }
   Gini_index[j]<-Ent
  j=j+1
}
  }

```

Calculated accuracy of the dataset to identify the column which will give better result while classiffying.


```{r}
Accuracy<-list()
j=0
for (i in colnames(Mush)){
  if(i!="V1") {
  E<-table(Mush[[i]],Mush$V1)
  S<-nrow(E)
  Ent<-list()
  for( K in 1:S) {
    
  Ent[K] =E[2,K]/sum(E[2,])
    
  }
   Accuracy[j]<-Ent[which.max(Ent)]
  j=j+1
}
  }
```

created dataset with all the above data

```{r}
j=0
column_names<-list()
for (i in colnames(Mush))
{
  if(i!="V1") {
    
  column_names[j] <- i
  j=j+1
  }
}
```

```{r}
C_name<-as.data.frame(unlist(column_names))
colnames(C_name)[1] <- "C_name"
```

```{r}
Accuracy<-as.data.frame(unlist(Accuracy))
colnames(Accuracy)[1] <- "Accuracy"
Gini_index<-as.data.frame(unlist(Gini_index))
colnames(Gini_index)[1] <- "Gini_index"
Entropy<-as.data.frame(unlist(Entropy))
colnames(Entropy)[1] <- "Entropy"

```

```{r}
Final<-cbind(C_name,Accuracy,Gini_index,Entropy)
  
```

```{r}
Final$Entropy<-1-Final$Entropy
```

Fina plot to check which columns are relevant.

```{r}
plot(Final$Entropy,Final$Accuracy)
with(Final, text(Entropy~Accuracy, labels = row.names(Final)))

```

NAive BAyers classifier loading library

```{r}
library(e1071)
library(rpart)

```



```{r}



testing<-read.csv("test.csv")
test<-break_columns(testing)


Mush_train<-Mush[c("V1","V10_b","V10_e","V10_k","V10_n","V10_o","V10_r","V10_u","V12_c","V12_r","V13_k","V14_k","V15_b","V15_c","V15_e","V15_g","V15_n","V15_o","V15_y","V16_b","V16_c","V16_e","V16_g","V16_n","V16_o","V16_y",
"V18_n","V18_o","V18_y","V19_n","V19_t","V2_b","V2_c","V2_s","V20_f","V20_l","V20_n","V21_b","V21_h","V21_k","V21_n","V21_o","V21_r","V21_u","V21_y","V22_a","V22_n","V23_m","V23_p","V23_w","V3_g","V6_m","V6_n","V6_s","V6_y","V7_a","V8_w","V9_n")]

Mush_test<-test[c("V1","V10_b","V10_e","V10_k","V10_n","V10_o","V10_r","V10_u","V12_c","V12_r","V13_k","V14_k","V15_b","V15_c","V15_e","V15_g","V15_n","V15_o","V15_y","V16_b","V16_c","V16_e","V16_g","V16_n","V16_o","V16_y",
"V18_n","V18_o","V18_y","V19_n","V19_t","V2_b","V2_c","V2_s","V20_f","V20_l","V20_n","V21_b","V21_h","V21_k","V21_n","V21_o","V21_r","V21_u","V21_y","V22_a","V22_n","V23_m","V23_p","V23_w","V3_g","V6_m","V6_n","V6_s","V6_y","V7_a","V8_w","V9_n")]


```



```{r}

accuracy_test<-list()
accuracy_train<-list()

for (i in 0:51)
{
Classify = naiveBayes(Mush_train[,2:58],Mush_train[,1],laplace=i)

Mush_train["predicted"]<-predict(Classify, Mush_train[,2:58])
Mush_test["predicted"]<-predict(Classify, Mush_test[,2:58])
accu_test<-table(Mush_test$predicted,Mush_test$V1)
accu_train<-table(Mush_train$predicted,Mush_train$V1)
#print(table(Mush_test$predicted))
accuracy_test[i]<-(accu_test[1]+accu_test[4])/nrow(Mush_test)
accuracy_train[i]<-(accu_train[1]+accu_train[4])/nrow(Mush_train)

Mush_train=subset(Mush_train, select = -c(predicted) )
Mush_test=subset(Mush_test, select = -c(predicted) )
}

```

```{r}
accuracy_test<-as.data.frame(unlist(accuracy_test))
colnames(accuracy_test)[1] <- "accuracy_test"
accuracy_train<-as.data.frame(unlist(accuracy_train))
colnames(accuracy_train)[1] <- "accuracy_train"
lambda<-seq(0,50)
lambda<-as.data.frame(unlist(lambda))
colnames(lambda)[1] <- "lambda"
Nb_accuracy<-cbind(lambda,accuracy_train,accuracy_test)

```

```{r}
plot(Nb_accuracy$lambda,Nb_accuracy$accuracy_train,type="l")
plot(Nb_accuracy$lambda,Nb_accuracy$accuracy_test,type="l")
```

```{r}
C<-seq(4,64,4)


accuracy_test_tree<-list()
accuracy_train_tree<-list()

for (i in list(C))
{
  tree1 <- rpart(V1 ~ ., data = Mush_train,method="class",control=list(maxdepth = i))
Mush_test['predicted']<-predict(tree1,Mush_test[,2:58],type="class")
Mush_train['predicted']<-predict(tree1,Mush_train[,2:58],type="class")
 accu_test<-table(Mush_test$predicted,Mush_test$V1)
accu_train<-table(Mush_train$predicted,Mush_train$V1)

accuracy_test_tree[i]<-(accu_test[1]+accu_test[4])/nrow(Mush_test)
accuracy_train_tree[i]<-(accu_train[1]+accu_train[4])/nrow(Mush_train)
 Mush_train=subset(Mush_train, select = -c(predicted) )
Mush_test=subset(Mush_test, select = -c(predicted) ) 
}
dim(Mush_train)
#plot(tree1)
```



```{r}
accuracy_test_tree<-as.data.frame(unlist(accuracy_test_tree))
colnames(accuracy_test_tree)[1] <- "accuracy_test_tree"
accuracy_train_tree<-as.data.frame(unlist(accuracy_train_tree))
colnames(accuracy_train_tree)[1] <- "accuracy_train_tree"
depth<-C
depth<-as.data.frame(unlist(depth))
colnames(depth)[1] <- "depth"
Dt_accuracy<-cbind(depth,accuracy_train_tree,accuracy_test_tree)

```

```{r}
plot(Dt_accuracy$depth,Dt_accuracy$accuracy_train_tree,type="l")
plot(Dt_accuracy$depth,Dt_accuracy$accuracy_test_tree,type="l")
```

